Geospatial - Assignment 3

### 2025-02-13 hw3/hw3_MoritzPeistNoemiLucchiSimonVellin.Rmd
knitted HTML

```{r}
# Package Loading
# Core data manipulation and visualization
library(tidyverse) # Data manipulation and visualization suite
library(ggplot2) # Advanced plotting (included in tidyverse)

# Spatial data handling
library(sf) # Simple Features for spatial vector data
library(spData) # Spatial datasets
library(terra) # Raster data handling
library(exactextractr) # Precise spatial averaging
library(gdistance) # Compute minimum distances on raster surfaces

# Additional utilities
library(units) # Unit handling and conversion
library(lwgeom) # Lightweight geometry operations
library(gridExtra) # Arranging multiple plots
library(readxl) # Excel file reading
```

@@

```{r}
# Load populated cities and roads
places <- st_read("/hw3/data/ne_10m_populated_places")
roads <- st_read("/hw3/data/ne_10m_roads")
```

>>>>

```{r}
# Package Loading
# Spatial data handling
library(sf) # Simple Features for spatial vector data
library(spData) # Spatial datasets
library(terra) # Raster data handling
library(exactextractr) # Precise spatial averaging
library(gdistance) # Compute minimum distances on raster surfaces

# Additional utilities
library(units) # Unit handling and conversion
library(lwgeom) # Lightweight geometry operations
library(gridExtra) # Arranging multiple plots
library(readxl) # Excel file reading

# Core data manipulation and visualization
library(tidyverse) # Data manipulation and visualization suite
library(ggplot2) # Advanced plotting (included in tidyverse)
```

@@

```{r}
# Load populated cities and roads
places <- st_read("data/ex2/ne_10m_populated_places")
roads <- st_read("data/ex2/ne_10m_roads")
```
